### 2012-05-16 inst/examples/cost_of_bias.Rmd
cost of bias

```{r }
set.seed(42)
sims_two <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

`` {r }
est_pars <- pars
par_var <- .1
````

@@

```{r }
set.seed(42)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- rnorm(1, pars[1], par_var)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r }
sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
````

@@

```{r }
set.seed(42)
sims_four <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

>>>>

```{r}
set.seed(42)
sims_two <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r}
est_pars <- pars
par_var <- .1
````

@@

```{r}
set.seed(42)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- rnorm(1, pars[1], par_var)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r}
sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
````

@@

```{r}
set.seed(42)
sims_four <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````
